### 2014-08-11 Neutral_simul.Rmd
Add KS comparison of DqSAD/SRS

# Load data if run only one chunk 
load(".RData")

@@

```{r simul_pomac467_T100,echo=F,message=F,warning=F}
setwd("Simul")

@@

# Which are not different
format(mks1[mks1$p.adjust>0.05,],digits=4)

den1 <- meltDensityOut_NT(paste0(bName,"T100Density.txt"),spMeta)
# Select a subset to test the procedure !
#
den1 <- den1[den1$MortalityRate==.2 & den1$DispersalDistance==0.04 & den1$ColonizationRate==0.001, ]

@@

rm(mks,psa)

@@

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="SRS",]

mks <- mks1[mks1$p.adjust<=0.05,]
# NO FUNCIONA MERGE
#psa <- mergePairSAD(mks[1,],Dq1)

@@

@@

m$compM

@@

setwd(oldcd)
rm(c1,c2,Dq2,Dq1)
rm(den1,den)
save.image()

@@

m <- compMethods_Time(bName,500,spMeta)

@@

@@

setwd(oldcd)
rm(c1,c2,Dq2)
rm(den1,den)
save.image()

@@

```{r simul_pomac467_T1000, eval=FALSE,echo=F,message=F,warning=F}
setwd("Simul")

@@

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- 1000
par[par$V1=="inter",]$V2 <- 1000 # interval to measure Density and Diversity
par[par$V1=="init",]$V2 <- 1000  # Firs time of measurement = interval
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff),"T1000")
par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters

@@

genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.01,0.1,1))

@@

s <- paste(neuBin,"sim.par","fishE.inp")
s
if(simul) system(s,wait=s_wait)

den1 <- meltDensityOut_NT("Exp467T1000Density.txt",nrow(ff))

mks1000 <- pairKS_SAD(den1)

# Which are not different
format(mks1000[mks1000$p.adjust>0.05,c(10:13,14:15)],digits=4)

# which is the proportion of not different
nrow(mks1000[mks1000$p.adjust>0.05,c(10:13,14:15)])/nrow(mks1000)

propNotDiffSAD(mks100)  
propNotDiffSAD(mks500)  
propNotDiffSAD(mks1000)  
```

@@

```{r boot_H_pomac467_T500,eval=FALSE,echo=F,message=F,warning=F}

@@

require(plyr)
require(boot)
require(vegan)

# den <- readWideDensityOut("Exp467T100Density.txt")
num_sp <- nrow(ff)
# how to apply a function to each row of a data frame
hh <- function(x) diversity(x[7:(6+num_sp)])
H <- apply(den,1,hh)

#H <- lapply(den,function(x) diversity(x[7:(6+num_sp)]))
#ldply(H)
# data.frame(colembolos = rowSums(spe[,1:5]), acaros=rowSums(spe[,6:33]),lombrices=rowSums(spe[,34:41]))
den[c(1,7),c("H","Richness")]
den[c(2,4),c("H","Richness")]

difh <- den[c(2,4),7:(6+num_sp)]*(500*500)
difh <- H_bss(difh)

print(difh)
summary(difh)

ciH <-ddply(s_col,.(Ambiente),function(df) boot_shannon(df[,1:5]) )

@@

>>>>

require(pander)
panderOptions('table.split.table',Inf)

@@

```{r simul_pomac467_T100, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

@@

# Which are not different
pander(mks1[mks1$p.adjust>0.05,],caption="SAD not different")

den1 <- meltDensityOut_NT(paste0(bName,"T100Density.txt"),spMeta)
# Select a subset to test the procedure !
#
#den1 <- den1[den1$MortalityRate==.2 & den1$DispersalDistance==0.04 & den1$ColonizationRate==0.001, ]

@@

rm(mks,psa,den2,den3)

@@

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="SRS" & mks1$p.adjust>0.05,]
pander(mks1,split.tables=Inf,caption="SRS not different")

# NO FUNCIONA MERGE
#psa <- mergePairSAD(mks[1,],Dq1)

@@

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
pander(mks1,caption="DqSAD not different")

@@

@@

setwd(oldcd)
rm(c1,c2,Dq2,Dq1)
rm(den1,den,mks1,mks,mks100)
save.image()

@@

m <- compMethods_Time(bName,1000,spMeta)

@@

pander(compM,caption="Proportion of not different")

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
pander(mks1,caption="DqSAD not different T=1000")

Dq1 <- readNeutral_calcDq(paste0(bName,"T1000mfSAD.txt"))

mergePair_plotDq(mks1[1,],Dq1,"DqSAD not different T=1000")

@@

mks1 <- mPval[mPval$method=="DqSAD" & mPval$p.adjust>0.05,]

setwd(oldcd)
rm(m,mks1)
save.image()

@@

```{r simul_pomac467_T1000, eval=T,echo=F,message=F,warning=F}

# Load data if run only one chunk 
#load(".RData")

if(simul)
{
  # Delete old simulations
  system("rm Exp467T1000*")

@@

  # Number of time steps 
  par[par$V1=="nEvals",]$V2 <- 1000
  par[par$V1=="inter",]$V2 <- 1000 # interval to measure Density and Diversity
  par[par$V1=="init",]$V2 <- 1000  # Firs time of measurement = interval
  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
  par[par$V1=="baseName",]$V2 <- paste0("Exp",spMeta,"T1000")
  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                                # 1:several simulations with pomac.lin parameters

@@

@@

  s <- paste(neuBin,"sim.par","fishE.inp")
  s
  if(simul) system(s,wait=F)
}

m <- compMethods_Time(bName,1000,spMeta)

pander(compM,caption="Proportion of not different")

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
pander(mks1,caption="DqSAD not different T500")

setwd(oldcd)
rm(m,mks1)
save.image()

@@

```{r plot_Time_pomac467,eval=T,echo=F,message=F,warning=F}

@@

# Plot different SAD with time

# Plot different Dq SRS with time

Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfOrd.txt"))
Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T500mfOrd.txt")))
Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T1000mfOrd.txt")))

mks1 <- mPval[mPval$method=="SRS" & mPval$p.adjust>0.05,]

mergePair_plotDq(mks1[1,],Dq1,"SRS not different")

mks1 <- mPval[mPval$method=="SRS" & mPval$p.adjust<=0.05,]

mergePair_plotDq(mks1[4,],Dq1,"SRS different")

# Plot different Dq SAD with time

Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))
Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T500mfSAD.txt")))
Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T1000mfSAD.txt")))

mks1 <- mPval[mPval$method=="DqSAD" & mPval$p.adjust>0.05,]

mergePair_plotDq(mks1[1,],Dq1,"DqSAD not different")

mks1 <- mPval[mPval$method=="DqSAD" & mPval$p.adjust<=0.05,]

mergePair_plotDq(mks1[4,],Dq1,"DqSAD different")

setwd(oldcd)

@@

```{r compKS_pomac467,eval=T,echo=F,message=F,warning=F}
source("R/Neutral_fun.r")

m <- compMethod_DqKS_Time(bName,100,spMeta)

pander(compM,caption="Proportion of not different")

m <- compMethod_DqKS_Time(bName,500,spMeta) 
compM <- rbind(compM,m$compM)
pander(compM,caption="Proportion of not different")
mPval <- rbind(mPval,m$mPval)

m <- compMethod_DqKS_Time(bName,1000,spMeta) 
compM <- rbind(compM,m$compM)
pander(compM,caption="Proportion of not different")
mPval <- rbind(mPval,m$mPval)

setwd(oldcd)

rm(m)

save.image()

names(mPval)
unique(mPval$method)
m <- with(mPval,mPval[method=="DqSADKS" & time==100,])
propNotDiffSAD(m)
